Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras

### 2019-07-26 tex/Rough-Overview.tex
Generalized code, got arguments in outline (minus Miles) to current

\title{Rough Cut of Proven Work on $\SH$.}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

@@

Throughout the text, we will refer to partitions of $2n + r$;
identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.

Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta(i,j)$ be the hook length
\[
  \beta(i,j) = \lambda_i - \lambda_j + \sum_{t = i}^j a_t.
\]
Then, adopting Kleshev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).

@@

\begin{figure}
  \[
    \begin{tabular}{l l}
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{2}{1/4, 2/3}{5/1,6/2}{(1+q)}
      \hspace{20pt}
      &
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{3}{1/2, 3/4}{5/1,6/2}{q^{1/2}}\\
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
      &
      \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
    \end{tabular}
  \]

@@

\subsection{Fibonacci Representation}
Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{*,p}^{n+1}$ such that the character $*$ never appears twice in a row. 
We will surpress the superscript whenever it is clear from context.

We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:
\def\vara{\alpha}
\def\varb{\beta}
\def\varc{\gamma}
\def\vard{\delta}
\def\vare{\varepsilon}

\begin{equation}
  \begin{split}
  T_1 \, (*pp) &:= \vara(*pp)\\
  T_1 \, (pp*) &:= \vara(pp*)\\
  T_1 \, (*p*) &:= \varb(*p*)\\
  T_1 \, (p*p) &:= \varc(p*p) + \vard(ppp)\\
  T_1 \, (ppp) &:= \vard(p*p) + \vare(ppp)
\end{split} \label{Fib Action} 
\end{equation}
for constants
\begin{equation}
  \begin{split}
  \vara &= -1\\
  \varb &= q\\
  \varc &= \tau(q\tau - 1)\\
  \vard &= \tau^{3/2}(q + 1)\\
  \vare &= \tau(q-\tau)\\
  \tau &= -1-q^2-q^3
\end{split} \label{Fib Constants} 
\end{equation}
with $T_i$ acting similarly on the substring $i,i+1,i+2$.
We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}

This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
Label the subrepresentation of strings $(*\dots*)$ by $V_{**}$, and similar for the other 3.
It is easy to see that $V_{*p} \simeq V_{p*}$, so that
\[
  V \simeq 2V_{*p} \oplus V_{**} \oplus V_{pp}.
\]
We will show that $V_{pp} \simeq V_{*p} \oplus V_{**}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
\begin{equation}
  \begin{split}    
    V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
    V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
    V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
    V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
  \end{split} \label{Fib Isos}
\end{equation}

\newpage
\section{Crossingless Matchings and Specht Modules}
Our goal is to prove that $W_{2n + r}^r \simeq S^{(n+r,n)'}$ when $e > n + r + 1$.
\begin{proposition}
  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $n,r > 0$.
    Then, a filtration of $\Res W_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
    \end{equation}
    with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
      \end{equation}
  \end{enumerate}
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.

@@

\begin{lemma}
  Every basis vector in $W_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

@@

  We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ sumbatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
  \[
    B_{n + r} := \begin{bmatrix}
      \begin{matrix}
      q + 1 & q^{1/2} & \\
      q^{1/2} & q + 1 & q^{1/2}\\
      & q^{1/2} & q + 1 & q^{1/2}\\
      &  & \ddots & \ddots
      \end{matrix}
      &   \bigzero\\
      \bigzerotwo & \begin{matrix}
        q^{1/2} & q+1 & q^{1/2}\\
        &  q^{1/2} & q + 1
       \end{matrix}
    \end{bmatrix}.
  \]
  We will show that this matrix is invertible;
  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on column $j$, giving $K = 0$.

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so supose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}

\begin{proposition}
  The representation $W_{2n + r}^r$ is irreducible when $e > n + r + 1$. 
\end{proposition}
\begin{proof}
  We proceed by induction on $2n + r$.
  Note that, by identification with the trivial and sign representations, the base case $2n + r = 2$ is already prove, so suppose we have proven this for each $2m + s < 2n + r$.

@@

\iffalse
The next piece in our puzzle is to characterize the restrictions of $W$ to $\SH' := \SH_{k,q}(S_{2n + r - 1}) \subset \SH$.
Recall that, when $r,n>0$ and $\SH$ is semisimple,  $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
Further, note that $S^{(n+r,n)'}$ is the unique irreducible having this restriction.

Next, note that we have already proven the correspondence for $W_{2n}^0$;
for $W_{0 + r}^{r}$, this is the sign representation, which is given correctly by $S^{(r)}$.
Hence, pending information on restrictions, we may prove this via induction on $2n + r$.
\fi

@@

\begin{theorem}
  Suppose $e > n + r + 1$, $n > 0$.
  Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
\end{theorem}
\begin{proof}
  By irreducibility, we know that $W_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  We will proceed in two steps;
  first we prove that $\lambda = (n+r,n)'$, then we prove that $S^{(n+r,n)'}$ is irreducible.

  This will be done inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e. $e > m + s + 1$).

  \def\thmsep{7pt}
  \vspace{\thmsep}
  \textit{Step 1.}
  By the inductive hypothesis and irreducibility, we have a composition series given by 
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)'} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)'} \longrightarrow 0
  \end{equation}
  In particular, by the Jordan-H\"older theorem, if we have some module $D^\mu \subset \Res \, D^\lambda$, then $\mu = (n+r-1,n)'$ or $\mu = (n+r,n-1)'$.

  By Kleschev, we know that $\soc(D^\lambda) = \bigoplus_{\mu} D^\mu$, where $\mu$ ranges over $\lambda(i)$ for every good number $i$ of $\lambda$.
  Immediately this narrows down $\lambda$ to three options;
  the only $\lambda$ with some $\lambda(i)$ giving $(n + r - 1,n)'$ are $\lambda_1 ;= (n+r-1,n,1)'$, $\lambda_2 = (n+r-1,n+1)'$, and $\lambda_3 = (n+r,n)'$.

  Note numbers $\beta_l(i,j)$ correspond to hook-lengths, and each $\lambda_;$ has maximum hook length $n + r + 1$;
  hence $\beta_l(i,j) \not\equiv 0 \pmod e$ for all $i,j,l$, and 3 is a good number in $\lambda_1$ and 2 in $\lambda_2$.
  This implies $D^{(n+r-2,n,1)'} \subset D^{\lambda_1}$ and $D^{(n+r-2,n+1)'} \subset D^{\lambda_2}$, giving that $\lambda = \lambda_3$ as desired.

>>>>

\title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules  of Hecke Algebras}
\author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
  Mentor Oron Propp\\
Project Suggested by Roman Bezrukavnikov\\ \; \\
July 31, 2019
}

\begin{titlepage}
  \maketitle
  \begin{abstract}
  Abstract goes here
  \end{abstract}
\end{titlepage}

@@

Throughout the text, we will refer to partitions of $2n + r$;
identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshchev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.

Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta(i,j)$ be the hook length
\[
  \beta(i,j) = \lambda_i - \lambda_j + \sum_{t = i}^j a_t.
\]
Then, adopting Kleshchev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).

@@

\begin{figure}[b]
  \[
    \begin{tabular}{l l}
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{2}{1/4, 2/3}{5/1,6/2}{(1+q)}
      \hspace{20pt}
      &
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{3}{1/2, 3/4}{5/1,6/2}{q^{1/2}}\\
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
      &
      \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
    \end{tabular}
  \]

@@

\subsection{Fibonacci Representation}
\def\vara{\alpha}
\def\varb{\beta}
\def\varc{\gamma}
\def\vard{\delta}
\def\vare{\varepsilon}
\def\vs{\texttt{*}}
\def\vp{\texttt{0}}
Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the character $\vs$ never appears twice in a row. 
We will suppress the superscript whenever it is clear from context.

We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:

\begin{equation} 
  \begin{split}
    T_1 \, \prn{\vs\vp\vp} &:= \vara\prn{\vs\vp\vp}\\
    T_1 \, \prn{\vp\vp\vs} &:= \vara\prn{\vp\vp\vs}\\
    T_1 \, \prn{\vs\vp\vs} &:= \varb\prn{\vs\vp\vs}\\
    T_1 \, \prn{\vp\vs\vp} &:= \varc\prn{\vp\vs\vp} + \vard\prn{\vp\vp\vp}\\
    T_1 \, \prn{\vp\vp\vp} &:= \vard\prn{\vp\vs\vp} + \vare\prn{\vp\vp\vp}
\end{split} \label{Fib Action} 
\end{equation}
for constants
\begin{equation}
  \begin{split}
  \vara &= -1\\
  \varb &= q\\
  \varc &= \tau(q\tau - 1)\\
  \vard &= \tau^{3/2}(q + 1)\\
  \vare &= \tau(q-\tau)\\
  \tau &= -1-q^2-q^3
\end{split} \label{Fib Constants} 
\end{equation}
with $T_i$ acting similarly on the substring $i,i+1,i+2$.
We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}

This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, and similar for the other 3.
It is easy to see that $V_{\vs\vp} \simeq V_{\vp\vs}$, so that
\[
  V \simeq 2V_{\vs\vp} \oplus V_{\vs\vs} \oplus V_{\vp\vp}.
\]
We will show that $V_{\vp\vp} \simeq V_{\vs\vp} \oplus V_{\vs\vs}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
\begin{equation}
  \begin{split}    
    V^{2n}_{\vs\vs} &\simeq D^{(n,n)'}\\ 
    V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)'}\\
    V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)'}\\
    V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)'}.
  \end{split} \label{Fib Isos}
\end{equation}

\newpage
\section{Preliminaries on Specht Modules}
\begin{proposition}
  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $n,r > 0$.
    Then, a filtration of $\Res W_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
     \end{equation}
     with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
       \end{equation}
  \end{enumerate}
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.

@@

\begin{lemma}
  Suppose $n,r > 0$.
  Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
  \[
    \soc\prn{\Res \, D^{(n+r,n)'}} \simeq \begin{cases}
      D^{(n + r - 1,n)'} & e \mid r+2\\
      D^{(n + r,n-1)'} & e \nmid r+2, \; e \mid r\\
      D^{(n+r-1,n)'} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
    \end{cases}
  \]
\end{lemma}
\begin{proof}
  This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
  \begin{align*}
    \beta_\lambda(1,2) &= r + 2\\
    \gamma_\lambda(1,2) &= r
  \end{align*}
  Since $2$ is the largest removable number, $D^{(n+r,n-1)'} \subset D^{(n+r,n)'}$ iff $e \nmid r + 2$.
  Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)'} \subset D^{(n+r,n)'}$ iff 1 is good iff $e \nmid r$
\end{proof}

\begin{lemma}\label{S irreducibility}
  \begin{enumerate}[label={(\roman*)}]
    Assume $e > 2$ and $n > 0$.
    \item Suppose $e > n$.
      Then, $S^{(n+r,n)'}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
    \item Suppose $e \leq n$.
      Then, $S^{(n+r,n)'}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values over rows $a \leq n$.
  \end{enumerate}  
\end{lemma}
\begin{proof}
  \textbf{(i)}
  Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the first column may vanish mod $e$;
  hence we may equivalently prove that $e$ divides no hook lengths in the first $n$ rows of the first column.
  These hook lengths are precisely $r + 2,\dots,n+r+1$.

  \textbf{(ii)}
  Note that we have $\nu_{e,p}\prn{h^\lambda_{n-e+1,2}} \neq -1$.
  Suppose that $e \nmid r + 1$.
  Then, \[\nu_{e,p}\prn{h^\lambda_{n-e+1,1}} = \nu_{e,p}\prn{h^\lambda_{n-e,2} + r + 1} = -1,\]
  giving $S^{(n+r,n)'}$ reducible.

  Note that $\nu$ acquires at least two values since $e$ is a hook length.
  Now, suppose that \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)'}$ is irreducible.
  If $a=a'$ then we have reducibility, so assume $a \neq a'$.
  Further, if $b = b'$, then we may replace $b$ with the other column;
  hence we may assume WLOG that $b \neq b'$ as well.

  Note that $p$-adic valuation is monotonic, so $h^\lambda_{ab} < h^\lambda_{a'b'}$.
  If $b < b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'}) < \nu(h_{a'b'})$ while $h_{ab'} > h_{a'b'}$, a contradiction.
  If $b > b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'})$ and $h_{ab} < h_{ab'}$, so there is some $c < b$ with $\nu_{e,b}(h_{ab}) = \nu_{e,p}(h_{ac})$; we may replace $b$ with $c$, and repeat until $b = b'$ to reach contradiction.

  Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values over the top $n$ rows.
  Since $e | r + 1$, $e \mid h_{a1}^\lambda$ iff $e \mid h_{a2}$;
  since $\nu_{e,p}$ acquires only two values, this proves that $\nu_{e,p}(h_{a1}) = \nu_{e,p}(h_{a2})$ across these rows, giving the lemma.
\end{proof}

This is complicated and annoying, and the second amounts to a condition on $p$.
We will illustrate that irreducibility interpolates between $p = 2$ and $p$ large:
\begin{corollary}
  Assume $2 < e \leq n$.
  \begin{enumerate}[label={(\roman*)}]
    \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)'}$ is irreducible iff $e | r + 1$.
    \item Suppose $p = 2$. Then, $S^{(n+r,n)'}$ is not irreducible.
  \end{enumerate}
\end{corollary}
\begin{proof}
  (i) is clear.
  (ii) is given by noting that $e + r + 1 \geq 2e$;
  then, $h_{n-e+1,1} - h_{n-e+1,2} \geq 1$, giving reducibility.
\end{proof}

\begin{proposition}\label{Combinatorics}
  Suppose that $e,n,r$ satisfy criterion (i) of Proposition \ref{S irreducibility}.
  Let $\lambda$ be a partition of $2n + r$.
  \begin{enumerate}[label={(\roman*)}]
    \item Suppose $r > 0$.
      If $D^\lambda$ has the composition series 
      \begin{equation}\label{D Composition Series}
        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
      \end{equation}
      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
    \item Suppose $r = 0$ and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
      Then $\lambda = (n,n)'$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)'$, and let $\mu := (n + r,n)'$.
  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.

  We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series};
  then, we will have $\lambda = \mu$.

  First, we focus on $\varpi$;
  Suppose $r > 1$ and $e \mid n + 1$;
  then, $\beta_{\varpi}(2,3) = n + 1 \equiv 0 \pmod e$, so $3$ is not normal and $D^{(n+r-1,n)'}$ is not in the socle of $D^\varpi$, giving $\lambda \neq \varpi$.

  Now suppose $r > 1$ and $e \nmid n + 1$.
  Then $S^{(n+r-2,n,1)'} \simeq D^{(n+r-2,n,1)'}$.
  Then, we have $D^{(n + r - 2,n,1)'} \simeq S^{(n + r - 2,n,1} \subset \Res \, D^{\varpi}$ since 1 is normal;
  this is not a composition factor in \eqref{D Composition Series}, so $\lambda \neq \varpi$.

  Similarly, assume $r = 1$;
  then, by the same logic, $D^{(n+r-1,n)'} \not\subset \Res \, D^\varpi$ or $D^{(n,n-1,1)} \subset \Res \, D^\varpi$, also implying $\lambda \neq \varpi$.
  \iffalse % keeping just in case
  \begin{align*}
    \beta_{\varpi}(1,2)     &= r + 1 \\
    \beta_{\varpi}(1,3)     &= n + r + 1 \\
    \beta_{\varpi}(2,3)     &= n + 1\\
    \gamma_{\varpi}(1,2)    &= r\\
    \gamma_{\varpi}(1,3)    &= n + r\\
    \gamma_{\varpi}(2,3)    &= n\\
  \end{align*}
  \fi

  \vspace{5pt}
  Now, focus on $\varsigma$;
  if $r < 2$, then $\varsigma$ is not a partition.
  If $r = 2$, then $\Res \, D^\varsigma \simeq D^{(n+1,n)'}$ is irreducible, contradicting \eqref{D Composition Series}. 
  If $r > 2$, then $D^{(n + r - 2,n+1)'}$ is irreducible, so $D^{(n+r-2,n+1)'} \simeq S^{(n+r-2,n+1)'} \subset D^\varsigma$, contradicting \eqref{D Composition Series}.

  \textbf{(ii)}
  This result is fundamentally similar to the previous result;
  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number, which pins $\lambda$.
\end{proof}

\iffalse
\begin{proposition}
  Suppose that $n > 0$ and $e \nmid n + r$.
  \begin{enumerate}[label={(\roman*)}]
    \item Suppose $r > 0$, $n > 1$, and either $e \nmid n + 1$ or $e \nmid n + r + 1, n + r - 1$.
      If $D^\lambda$ has the composition series 
      \begin{equation}\label{D Composition Series}
        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
      \end{equation}
      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
    \item Suppose $n = 1$ and $e \nmid r+2$, and suppose that we have composition series \eqref{D Composition Series}.
      Then $\lambda=(r+1,r+2)'$.
    \item Suppose $r = 0$, either $e \nmid n+2$ or $e > 3$, and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
      Then $\lambda = (n,n)'$.
  \end{enumerate}
  The above conditions are unilaterally met whenever $e > n + r + 1$ and $(n,r) \neq (1,0)$.
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Let $\lambda_1 := (n+r-1,n,1)$, let $\lambda_2 := (n+r-1,n+1)'$, and let $\lambda_3 := (n + r,n)'$.
  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \lambda_i$ for some $i = 1,2,3$.
  We will show that $\lambda_1,\lambda_2$ each have good numbers other than 1, leading to elements of their socle that are not factors in \eqref{D Composition Series};
  then, we will have $\lambda = \lambda_3$.

  We may straightforwardly compute this.
  First assume $n \geq 2$, so that
  \begin{align*}
    \beta_{\lambda_1}(1,2) &= n + 1\\
    \beta_{\lambda_1}(1,3) &= n + r + 1\\
    \beta_{\lambda_1}(2,3) &= n + r - 1\\
    \beta_{\lambda_2}(1,2) &= n + r
  \end{align*}

  \textbf{(ii)}
  The choices are the same as above, but now $\lambda_1$ only has two removable nodes, so that
  \begin{align*}
    \beta_{\lambda_1}(1,3) &= r + 2\\
    \beta_{\lambda_2}(1,2) &= r + 1
  \end{align*}

  \textbf{(iii)}
  Let $\lambda_1 := (n,n-1,1)'$, let $\lambda_2 := (n+1,n-1)'$, and let $\lambda_3 := (n,n)'$;
  as before we know that $\lambda = \lambda_i$ for $i = 1,2,3$, so we will eliminate $\lambda_1,\lambda_2$.
  First, we will show that $\lambda_1$ has a good number other than 1:
  \begin{align*}
    \beta_{\lambda_1}(1,2) &= n\\
    \beta_{\lambda_1}(1,3) &= n + 2\\
    \beta_{\lambda_1}(2,3) &= n\\
  \end{align*}
  Hence we may rule out $\lambda_1$ when $e | n$.

  Suppose $D^{\lambda_2}$ satisfies the isomorphism;
  then the number 2 is normal.
  We may make the following computations:
  \begin{align*}
    \beta_{\lambda_2}(1,2) &= n + 2\\
    \gamma_{\lambda_2}(1,2) &= 3.
  \end{align*}
  When $e | n + 2$, this brings contradiction;
  when $e \nmid n + 2$ and $e > 3$, 2 is a good number (recalling that $e > 2$), giving non-semisimple restriction, a contradiction.
  Hence $\lambda = \lambda_3$ and the proposition is proven.
\end{proof}
\fi

\section{Crossingless Matchings and Specht Modules}
\subsection{Preliminaries on Crossingless Matchings}
\begin{lemma}
  \label{Cyclic}
  Every basis vector in $W_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

@@

  We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ submatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
  \begin{equation}\label{Bnr}
    B_{n + r} := \begin{bmatrix}
      \begin{matrix}
      q + 1 & q^{1/2} & \\
      q^{1/2} & q + 1 & q^{1/2}\\
      & q^{1/2} & q + 1 & q^{1/2}\\
      &  & \ddots & \ddots
      \end{matrix}
      &   \bigzero\\
      \bigzerotwo & \begin{matrix}
        q^{1/2} & q+1 & q^{1/2}\\
        &  q^{1/2} & q + 1
       \end{matrix}
    \end{bmatrix}.
  \end{equation}
  We will show that this matrix is invertible;
  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on column $j$, giving $K = 0$.

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}

\subsection{Correspondence}
\begin{proposition}
  The representation $W_{2n + r}^r$ is irreducible when $e > n + r + 1$. 
\end{proposition}
\begin{proof}
  We proceed by induction on $2n + r$.
  Note that, by identification with the trivial and sign representations, the base case $2n + r = 2$ is already prove, so suppose we have proven this for each $2m + s < 2n + r$.

@@

@@

\begin{theorem}
  Suppose $e > n + r + 1$.
  Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
\end{theorem}
\begin{proof}
  The case $n = 0$ is already proven, so suppose $n > 0$.

  By irreducibility, we know that $W_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e. $e > m + s + 1$).

  By the inductive hypothesis and irreducibility, we have a composition series given by 
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)'} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)'} \longrightarrow 0
   \end{equation}
  Hence the theorem is given by Proposition \ref{Combinatorics}.
\end{proof}

\iffalse
We may reuse the above structure of proof as above;
suppose $W_{2n + r}^r$ and $S^{(n+r,n)'}$ are irreducible, and $\lambda = (n+r,n)'$ is the unique diagram having composition series \eqref{Composition Series}.
Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.

We have covered all irreducible cases for $r = 0$ and $n = 0$ above.
For example, another case where we may show all irreducible cases is $n = 1$, which we will do now.
\begin{lemma}\label{n=1 irreducibility}
    Set $n = 1$. 
    Then $W_{2 + r}^r$ is irreducible iff $e \nmid r + 2$.
\end{lemma}
\begin{proof}
  A basis element $w_i \in W$ is determined entirely by the position of the arc, of which there are $r + 1$ options.
  Hence $\dim W = r + 1$.

  Further, $\dim\prn{\ima (1 + T_i)} = 1$ for all $i$;
  by lemma \ref{Cyclic} $W$ is irreducible iff $K := \bigcap_{i = 1}^{r+1} \ker (1 + T_i) = \ker \bigoplus (1 + T_i)$ is trivial.
  By \ref{Trivial}, this is true iff $e \nmid r + 2$.
\end{proof}
